---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
    collapse = TRUE,
    comment = "#>",
    fig.path = "man/figures/README-",
    out.width = "70%"
)
```

# concordexR

<!-- badges: start -->
[![codecov](https://codecov.io/gh/pachterlab/concordexR/branch/main/graph/badge.svg?token=FSASJPR4T5)](https://codecov.io/gh/pachterlab/concordexR)
<!-- badges: end -->


The goal of concordexR is to identify spatial homogeneous regions (SHRs) as 
defined in the recent manuscript, ["Identification of spatial homogenous regions in tissues with concordex"](https://doi.org/10.1101/2023.06.28.546949). Briefly, SHRs are are 
domains that are homogeneous with respect to cell type composition. `concordex` 
relies on the the k-nearest-neighbor (kNN) graph to representing similarities 
between cells and uses common clustering algorithms to identify SHRs.

## Installation

(Recommended) You can install the development version of `concordexR` from
[GitHub](https://github.com/) with:

```{r}
# install.packages("devtools")
devtools::install_github("pachterlab/concordexR")
```

Versions of the `concordexR` package that do not enable clustering spatial data
into spatial homogeneous regions (SHRs) are available for Bioconductor versions
3.17-19. The most recent version of the package is slated to be released on 
Bioconductor version 3.20. You can install the Bioconductor development version 
with: 

```{r}
if (!requireNamespace("BiocManager", quietly = TRUE))
    install.packages("BiocManager")
    
BiocManager::install(version="devel")
BiocManager::install("concordexR")
```

## Example

This is a basic example using concordex:

```{r load libraries}
library(SFEData)
library(Voyager)
library(scran)
library(bluster)

library(concordexR)
```

```{r}
sfe <- McKellarMuscleData("small")
clusters <- quickCluster(sfe, min.size=2, d=15)
```

```{r example}
nbc <- calculateConcordex(
    sfe,
    clusters,
    n_neighbors=10,
    BLUSPARAM=KmeansParam(2)
)

colData(sfe)[["shr"]] <- attr(nbc, "shrs")
```

```{r plot-shr}
plotSpatialFeature(sfe, features="shr")
```

## Citation

If you'd like to use the `concordexR` package in your research, please cite our
recent bioRxiv preprint

>  Jackson, K.; Booeshaghi, A. S.; Gálvez-Merchán, Á.; Moses, L.; Chari, T.; Pachter, L. Quantitative assessment of single-cell RNA-seq clustering with CONCORDEX. bioRxiv (Cold Spring Harbor Laboratory) 2023. https://doi.org/10.1101/2023.06.28.546949.

   @article {Jackson2023.06.28.546949,
	author = {Jackson, Kayla C. and Booeshaghi, A. Sina and G{\'a}lvez-Merch{\'a}n, {\'A}ngel and Moses, Lambda and Chari, Tara and Kim, Alexandra and Pachter, Lior},
	title = {Identification of spatial homogeneous regions in tissues with concordex},
	year = {2024},
	doi = {10.1101/2023.06.28.546949},
	publisher = {Cold Spring Harbor Laboratory},
	URL = {https://www.biorxiv.org/content/early/2024/07/18/2023.06.28.546949},
	journal = {bioRxiv}
}
    
## Maintainer

[Kayla Jackson](https://github.com/kayla-jackson)
